### 2025-01-08 paper/icml25/first/sects/experiments.tex
minor on experiment section
compact the networks description a bit (@f14-bertolotti check pls)

\section{experiments}\label{sect:experiments}

\paragraph{Scenarios}
As mentioned previously, we choose a few multi-angent scenarios from the VMAS\footnote{\url{https://github.com/proroklab/VectorizedMultiAgentSimulator}} package to test \fname{} aganist SHAC and PPO. In particular, we choose the following scenario:
\begin{compactitem}
    \item \textbf{Dispersion}: a scenario where $n$ agents need to reach $n$ goal locations, in such case the agent rechieves a sparse reward of $1$. Agents observe only their own position, velocity and relative position to each goal. Despite the transition function being differentiable, the reward function is not. Therefore, only PPO and \fname{} are applicable to this scenario.
    \item \textbf{Transport}: a scenario where $n$ agents need to collaborate to push a package into a goal location. Agents observe their own position, velocity, relative position to the package and relative position between package and the goal. The agents receive a reward proportional to the distance between package and the goal. In this scenario, both the reward and transition functions are differentiable.
    \item \textbf{Sampling}: a scenario where $n$ agents need to collect rewards from a grid. The reward are sampled from $k$ gaussians. Agents observe their own position, velocity, lidar values to sence each other, and rewards in a 3x3 grid around themselves.  In this scenario, both the reward and transition functions are differentiable.
    \item \textbf{Discovery}: a scenario where $n$ agents need to collect $k$ goal place randomly. A goal is collected if at least $s$ agents stand in close proximity to it, in this case they receive a reward of $1$. If agents collide with each other, they receive a penalty. Every agent observes its position, velocity, lidar measurements to other agents and goals. In this scenario, only the transition function is differentiable. Therefore, only PPO and \fname{} are applicable to this scenario.
\end{compactitem}

\paragraph{Architectures}
We test SHAC, PPO, and \fname{} with the both a MLP and a Transformer architectures. In particular, we use the following:
\begin{compactitem}
    \item \textbf{Policy Network}: a 1-layer MLP with hidden size $64$ or a 1-layer single-head Transformer with hidden size $64$ (for PPO, SHAC, and \fname{}).
    \item \textbf{Value Network}:  a 1-layer MLP with hidden size $64$ or a 1-layer single-head Transformer with hidden size $64$ (for PPO, SHAC, and \fname{}).
    \item \textbf{Reward Network}: a 1-layer MLP with hidden size $64$ or a 1-layer single-head Transformer with hidden size $64$ (for \fname{}).
    \item \textbf{Transition Network}: a 3-layer single-head Transformer with hidden size $64$ (for \fname{}).
\end{compactitem}
While the MLP architecture is the most simple, the Transformer baseline benefits from position invariance property of the agents observations. We apply the transformer architecture only if the number of agents is greater than $1$, otherwise we use only the MLP architecture.

>>>>

\section{Experiments}\label{sect:experiments}

\paragraph{Scenarios}
As mentioned previously, we choose a few multi-agent scenarios from the VMAS\footnote{\url{https://github.com/proroklab/VectorizedMultiAgentSimulator}} package to test \fname{} aganist SHAC and PPO. In particular, we choose the following scenario:
\begin{compactitem}
    \item \textbf{Dispersion}: a scenario where $n$ agents need to reach $n$ goal locations, in such case the agent receives a sparse reward of $1$. Agents observe only their own position, velocity and relative position to each goal. Despite the transition function being differentiable, the reward function is not. Therefore, only PPO and \fname{} are applicable to this scenario.
    \item \textbf{Transport}: a scenario where $n$ agents need to collaborate to push a package into a goal location. Agents observe their own position, velocity, relative position to the package and relative position between package and the goal. The agents receive a reward proportional to the distance between package and the goal. In this scenario, both the reward and transition functions are differentiable.
    \item \textbf{Sampling}: a scenario where $n$ agents need to collect rewards from a grid. The reward are sampled from $k$ gaussians. Agents observe their own position, velocity, lidar values to since each other, and rewards in a 3x3 grid around themselves.  In this scenario, both the reward and transition functions are differentiable.
    \item \textbf{Discovery}: a scenario where $n$ agents need to collect $k$ goal place randomly. A goal is collected if at least $s$ agents stand in proximity to it, in this case they receive a reward of $1$. If agents collide with each other, they receive a penalty. Every agent observes its position, velocity, lidar measurements to other agents and goals. In this scenario, only the transition function is differentiable. Therefore, only PPO and \fname{} are applicable to this scenario.
\end{compactitem}

\paragraph{Architectures}
We test SHAC, PPO, and \fname{} with both an MLP and a Transformer architecture. Specifically, we use a 1-layer MLP with hidden size 64 or a 1-layer single-head Transformer with hidden size 64 for the Policy Network and Value Network (for PPO, SHAC, and \fname{}). For the Reward Network, we use a 1-layer MLP with hidden size 64 or a 1-layer single-head Transformer with hidden size 64 (for \fname{}). The Transition Network for \fname{} is a 3-layer single-head Transformer with hidden size 64.

While the MLP architecture is the simplest, the Transformer baseline benefits from position invariance property of the agents observations. We apply the transformer architecture only if the number of agents is greater than $1$, otherwise we use only the MLP architecture.
